Research log

### 2023-04-08 analysis/clickEntropyBattleship.Rmd
fixed entropy to log2 instead of log

```{r entropy-by-serial-position, echo=FALSE, cache=TRUE}

@@

```{r entropy-pclick-correlation, echo=FALSE, cache=TRUE}

E2.entropy_summary <- E2.click_entropy_by_serial_position %>%
  filter(click_number<8) %>%
  group_by(subj_id,test_part) %>%
  summarise(entropy=mean(entropy,na.rm=T))

E2.p_click_summary <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_random) %>%
  ungroup() %>%
  filter(click_number<8) %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click_rank=mean(p_click_rank))

>>>>

```{r battleship-entropy-by-serial-position, echo=FALSE, cache=TRUE}

@@

```{r battleship-entropy-pclick-correlation, echo=FALSE, cache=TRUE}

E2.entropy_summary <- E2.click_entropy_by_serial_position %>%
  filter(click_number<6) %>%
  group_by(subj_id,test_part) %>%
  summarise(entropy=mean(entropy,na.rm=T))

E2.p_click_summary <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_random) %>%
  ungroup() %>%
  filter(click_number<6) %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click_rank=mean(p_click_rank))

### 2023-04-08 analysis/clickEntropyHangman.Rmd
fixed entropy to log2 instead of log

```{r entropy-by-serial-position, echo=FALSE, cache=TRUE}

@@

e4.click_entropy_by_serial_position <- e4.click_log_with_boards %>%
  mutate(flat_position = which(LETTERS==letter)) %>%
  # filter(click_number<15) %>%
  group_by(subj_id,test_part,click_number)%>%
  summarise(entropy=entropy(flat_position))

e4.click_entropy_by_serial_position_summary <- e4.click_entropy_by_serial_position %>%
  group_by(test_part,click_number) %>%
  summarise(mean_entropy=mean(entropy, na.rm=T),
            se_entropy=se(entropy, na.rm=T)) %>%
  mutate(test_part = factor(test_part, levels=c('nonpretend','pretend','random','optimal')));

p <- e4.click_entropy_by_serial_position_summary %>%
  ggplot(aes(x=click_number,y=mean_entropy,color=test_part,group=test_part)) +
  geom_line() +
  geom_ribbon(aes(ymax=mean_entropy+se_entropy,ymin=mean_entropy-se_entropy, fill=test_part),alpha=0.5) +
  scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", "black")) +
  scale_color_manual(values=c("#69b3a2", "#404080", "black", "black")) +
  labs(x='click number', y='entropy') +
  theme_classic()

@@

>>>>

```{r hangman-entropy-by-serial-position, echo=FALSE, cache=TRUE}

@@

E4.click_entropy_by_serial_position <- E4.click_log_with_boards %>%
  mutate(flat_position = which(LETTERS==letter)) %>%
  # filter(click_number<15) %>%
  group_by(subj_id,test_part,click_number)%>%
  summarise(entropy=entropy(flat_position))

E4.click_entropy_by_serial_position_wide <- E4.click_entropy_by_serial_position %>%
  spread(test_part,entropy) %>% 
  mutate(diff=pretend-nonpretend)

E4.click_entropy_by_serial_position_summary <- E4.click_entropy_by_serial_position %>%
  group_by(test_part,click_number) %>%
  summarise(mean_entropy=mean(entropy, na.rm=T),
            se_entropy=se(entropy, na.rm=T)) %>%
  mutate(test_part = factor(test_part, levels=c('nonpretend','pretend','random','optimal')));

p <- E4.click_entropy_by_serial_position_summary %>%
  ggplot(aes(x=click_number,y=mean_entropy,color=test_part,group=test_part)) +
  geom_line() +
  geom_ribbon(aes(ymax=mean_entropy+se_entropy,ymin=mean_entropy-se_entropy, fill=test_part),alpha=0.5) +
  scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", "black")) +
  scale_color_manual(values=c("#69b3a2", "#404080", "black", "black")) +
  labs(x='click number', y='entropy') +
  theme_classic()

@@

```{r hangman-entropy-pclick-correlation, echo=FALSE, cache=TRUE}

E4.entropy_summary <- E4.click_entropy_by_serial_position %>%
  filter(click_number<6) %>%
  group_by(subj_id,test_part) %>%
  summarise(entropy=mean(entropy,na.rm=T))

E4.p_click_summary <- E4.click_log_with_boards %>%
  rbind(E4.click_log_with_boards_random) %>%
  ungroup() %>%
  filter(click_number<6) %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click_rank=mean(p_click_rank))

E4.entropy_cost <- E4.p_click_summary %>%
  merge(E4.entropy_summary)%>%
  group_by(subj_id)%>%
  summarise(p_click_cost = p_click_rank[test_part=='pretend']-
              p_click_rank[test_part=='nonpretend'],
            entropy_cost = entropy[test_part=='pretend']-
              entropy[test_part=='nonpretend'])

### 2023-04-08 docs/ExploratoryResults.Rmd
fixed entropy to log2 instead of log

get_posterior_entropy <- function(posterior) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  posterior[which(posterior==0)]=NA; #to avoid infinity*0
  entropy <- -sum(unlist(posterior)*(unlist(log(posterior))),na.rm=TRUE);
  return(entropy);
}

>>>>

get_posterior_entropy <- function(posterior) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  posterior[which(posterior==0)]=NA; #to avoid infinity*0
  entropy <- -sum(unlist(posterior)*(unlist(log2(posterior))),na.rm=TRUE);
  return(entropy);
}

### 2023-04-08 docs/hangman.Rmd
fixed entropy to log2 instead of log

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

@@

groundhog.library(c(
  'png',
  'grid',
  'ggplot2',
  'svglite',
  'xtable',
  'papaja',
  'tidyverse',
  'broom',
  'cowplot',
  'reticulate',
  'MESS', # for AUCs
  'lsr', # for effect sizes
  'pwr', # for power calculations
  'brms', # for mixed effects modeling
  'BayesFactor', # for Bayesian t test
  'jsonlite', # parsing data from sort_trial
  'caret', #for cross validation
  'ggrepel', #for ggplot words
  'caret' #for cross validation
  'kernlab' #for SVM
), '2022-12-01')

@@

bonus.df %>%
  filter(PROLIFIC_PID %in% export_3_ss)%>%
  filter(bonus>0)%>%
  dplyr::select(PROLIFIC_PID,bonus)%>%
  write.table('..\\experiments\\Hangman2\\data\\bonuses\\prolific_export3.csv', 
              sep=',',col.names = F, row.names=F, quote=F)

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::html_book
---

@@

groundhog.library(c(
  'png',
  'grid',
  'ggplot2',
  'svglite',
  'xtable',
  'papaja',
  'tidyverse',
  'broom',
  'cowplot',
  'reticulate',
  'MESS', # for AUCs
  'lsr', # for effect sizes
  'pwr', # for power calculations
  'brms', # for mixed effects modeling
  'BayesFactor', # for Bayesian t test
  'jsonlite', # parsing data from sort_trial
  'caret', #for cross validation
  'ggrepel', #for ggplot words
  'caret', #for cross validation
  'kernlab' #for SVM
), '2022-12-01')

@@

bonus.df %>%
  filter(PROLIFIC_PID %in% export_3_ss)%>%
  filter(bonus>0)%>%
  dplyr::select(PROLIFIC_PID,bonus)%>%
  write.table('..\\experiments\\Hangman2\\data\\bonuses\\prolific_export3.csv', 
              sep=',', row.names=F, quote=F)

### 2023-04-08 docs/preregisteredMethodsAndResults.Rmd
fixed entropy to log2 instead of log

word_is_consistent <- function(word_state, asked,  word) {

  word_state = strsplit(toupper(word_state),'')[[1]];
  word = strsplit(toupper(word),'')[[1]];
  asked = strsplit(toupper(asked),'')[[1]];
  not_in_word = asked[!(asked %in% word_state)]

  # check if number of letters is consistent
  if (length(word_state) != length(word)) {
    return(FALSE)
  }

  # check if the letters in the masked word are consistent
  for (i in seq_along(word)) {
    if (word_state[i] != word[i]) {
      if (word_state[i] != '_' | word[i] == ' ' | word[i] == '.') {
      return(FALSE)
      }
    }
  }

  # check if any of the misses appear in the candidate word
  if (length(Reduce(intersect,list(word,not_in_word)))>0) {
    return(FALSE)
  }

  #if the function hasn't returned FALSE, return TRUE
  return(TRUE)

@@

get_letter_posterior_entropy <- function(posterior) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  posterior[which(posterior==0)]=NA; #to avoid infinity*0
  entropy <- -sum(unlist(posterior)*(unlist(log(posterior))),na.rm=TRUE);
  return(entropy);
}

@@

# E4.letter_prob_click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>%
#   rowwise()%>%
#   mutate(posterior = get_letter_prob_posterior(asked),
#          p_click = get_p_letter(posterior,letter),
#          entropy = get_letter_posterior_entropy(posterior),
#          p_click_rank = get_p_letter_rank(posterior,letter));

@@

E4.click_log_with_boards %>%
  filter(click_number>1) %>%
  mutate(entropy_bin=round(entropy*3)/3) %>%
  group_by(test_part,subj_id,entropy_bin) %>% 
  summarise(RT=median(RT)) %>%
  group_by(test_part,entropy_bin) %>%
  summarise(median_RT=median(RT),
            sem_RT=bootstrap_error(RT,N_perm)) %>%
  ggplot(aes(x=entropy_bin,color=test_part,fill=test_part,y=median_RT)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_RT-sem_RT,ymax=median_RT+sem_RT),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='Entropy of posterior', y='median RT (ms)')+
  theme_classic()

>>>>

get_word_state <- function(word, asked) {
  word_state = ''
  for (letter in strsplit(word,'')[[1]]) {
    value <- ifelse(grepl(toupper(letter), paste(toupper(asked),' ', sep='')), letter, '_')
    word_state <- paste(word_state, value, sep='')
  }
  return(toupper(word_state))
}

word_is_consistent <- function(word_state, asked,  word) {
  return(get_word_state(word,asked)==toupper(word_state))
}

@@

get_letter_posterior_entropy <- function(posterior) {
    posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
    posterior[which(posterior==0)]=NA; #to avoid infinity*0
    entropy <- -sum(unlist(posterior)*(unlist(log2(posterior))),na.rm=TRUE);
    return(entropy);
  }

@@

# E4.letter_prob_click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>%
#   rowwise()%>%
#   mutate(posterior = get_letter_prob_posterior(asked),
#          p_click = get_p_letter(posterior,letter),
#          entropy = get_letter_posterior_entropy(posterior),
#          p_click_rank = get_p_letter_rank(posterior,letter));
#

@@

E4.click_log_with_boards %>%
  filter(click_number>1) %>%
  mutate(entropy_bin=round(entropy*2)/2) %>%
  group_by(test_part,subj_id,entropy_bin) %>% 
  summarise(RT=median(RT)) %>%
  group_by(test_part,entropy_bin) %>%
  summarise(median_RT=median(RT),
            sem_RT=bootstrap_error(RT,N_perm)) %>%
  ggplot(aes(x=entropy_bin,color=test_part,fill=test_part,y=median_RT)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_RT-sem_RT,ymax=median_RT+sem_RT),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='Entropy of posterior', y='median RT (ms)')+
  theme_classic()
